Compositional equivalences based on Open pNets\thanks{This work was partially funded by the Associated Team FM4CPS between INRIA and ECNU, Shanghai}

### 2019-07-03 2016-Weak-FH-Bisim/WeakBisim.tex
indices echanges pendant/apres le skype
Working on lemma 6

\begin{lemma}[Weak OT decomposition]\label{lem-decomposeWOT} 
	Let $\Leaves(Q)=pLTS_l^{l\in L_Q}$; suppose\footnote{Note that the hypotheses of the 
	lemma imply that $Q$ is 
	not a pLTS but a similar lemma can be proven for a pLTS $Q$}:
	\[ P[Q]_{j_0}  
		\models
		{\openrule
			{
				\gamma_j^{j\in J}, \Pred,  
				\Post}
			{\ostate{s_i^{i\in L}} \OTWeakarrow {\alpha}
				\ostate{s_i'^{\, i\in L}}}
		}
	\]
		with  $J\cap\Holes(Q)\neq\emptyset$ or $\exists i\in L_Q.\,s_i\neq s'_i$, i.e. $Q$ takes part in the reduction.  
		 Then there exist $n$, $\Pred\,'$,  
		$\Post\,'$,   and for all $p\in[0..n]$ there exist $\beta_p$, $\alpha_p$, $\Pred_p$, $\Post_p$ and a family $\gamma_{p j}^{j\in J_p}$ and for all $p\in[0..n+1]$ $s_{p i}^{\,i\in L_Q}$. s.t.:\\[-2ex]
		%\[
		\begin{mathpar}
		P\models{\openrule
			{
				\gamma_j^{j\in (J_p\setminus \Holes(Q)) \cup \{j_0\}}, 
				\Pred\,',  
				\Post\,'}
			{\ostate{s_i^{i\in L\setminus L_Q}} \OTWeakarrow {\alpha}
				\ostate{s_i'^{\,i\in L\setminus L_Q}}}
		}%\]
\text{\qquad and \qquad}\gamma_{j_0}=[\beta_0..\beta_n]
	\vspace{-2.2ex}\\\text{and for all $p\in[0..n]$~~}
		%\[
		Q\models{\openrule
			{
				\gamma_{p j}^{j\in J_p}, \Pred_p,  
				\Post_p}
			{\ostate{s_{p i}^{i\in L_Q}} \OTWeakarrow {\alpha_p}
				\ostate{s_{(p+1) i}^{\,i\in L_Q}}}
		}%\]
\\
		\text{and~~}  \bigcup_{p=0}^nJ_{p} = J\cap\Holes(Q) \qquad
 \text{and\qquad} \forall j\in J_p,\,\gamma_j= \mybigdotcup_{p=0}^n \gamma_{p j} \\
 \text{and\quad} \forall i \in L_Q.\, s_{(n+1) i} = s_i'\land s_{0 i} = s_i\\{\hspace{-3ex}}\text{and~~} \Pred = \Pred\,'
		\land \!\!\bigwedge_{p=0}^n((\alpha_p= \beta_p\land \Pred_p)\bigotimes_{i=p-1}^{0}\Post_i) 
\\
\text{and~}
\Post=\Post\,' \uplus \bigotimes_{p=0}^n
		\Post_p  
		\end{mathpar}
where $\Post_p$ only act upon variables of 
		$\Leaves(Q)$.
\end{lemma}

\begin{proof} Suppose that we have: 
\begin{mathpar}
 P[Q]_{j_0} \models \openrule
			{
				\gamma_j^{j\in J}, \Pred,  
				\Post}
			{\ostate{s_l^{l\in L}} \OTWeakarrow {\alpha'}
				\ostate{s_l'^{\, l\in L}}} 
\end{mathpar}
By Lemma \ref{lem-rel-OT-WOT} this implies the following: \\			
$ \forall p\! \in [0..m_1]\,		
	P[Q]_{j_0}\!\models		
\openrule
    {
       \set{\beta_{1p}},\Pred_{1p},\Post_{1p}   }
         {\ostate{s^{l\in L}_{pl}} \OTarrow {\tau} \ostate{s^{l\in L}_{(p+1)l}}}$,  $\qquad  P[Q]_{j_0}	\models \openrule
         {
           \set{\beta_2},\Pred_2,\Post_2 }
         {\ostate{t_l^{l\in L}} \OTarrow {\alpha} \ostate{{t'}_l^{l\in L}}}
$ 
\\
and 
 $\forall p \in [0..m_2] \,\, P[Q]_{j_0}\!\models \openrule
         {
           \set{\beta_{3p}},\Pred_{3p}, \Post_{3p}   }
         {\ostate{u^{l\in L}_{pl}} \OTarrow {\tau} \ostate{u^{l\in L}_{(p+1)l}}}
$\\
where for all $l\in L$:\\
$\alpha'=\alpha\displaystyle{\subst{\bigotimes_{j=m_1}^{0}\!\!\Post_{1j}}}$\\
$s_l=s_{0 l} \wedge s_{(m_1+1) l}=t_l \wedge t'_l = u_{0 l} \wedge u_{(m_2+1) l}=s'_l$\\
$\displaystyle{
\set{\gamma}=\mybigdotcup_{i=0}^{m_1} \vis{\set{\beta_{1i}}\subst{\bigotimes_{j=i-1}^{0}\!\! \Post_{1j}}}\dotcup  \vis{\set{\beta_2}\subst{\bigotimes_{j=m_1}^{0}\Post_{1j}}} \dotcup \mybigdotcup_{i=0}^{m_2} \vis{\set{\beta_{3i}} \subst{\bigotimes_{j=i-1}^{0}\!\Post_{3j}\shortotimes\Post_2\shortotimes\bigotimes_{j=m_1}^{0}\!\!\Post_{1j}} }}
\\
\Pred=\bigwedge_{i=0}^{m_1}\Pred_{1i}\subst{\bigotimes_{j=i-1}^{0}\!\!\Post_{1j}}\land\Pred_2 \subst{\bigotimes_{j=m_1}^{0}\!\!\Post_{1j}}\land\\ 
~\qquad\quad\bigwedge_{i=0}^{m_2}\Pred_{3i}\subst{\bigotimes_{j=i-1}^{0}\!\!\Post_{3j}\shortotimes\Post_2\shortotimes\bigotimes_{j=m_1}^{0}\!\!\Post_{1j}}\\
\Post=\bigotimes_{j=m_2}^{0}\!\!\Post_{3j}\shortotimes\Post_2\shortotimes\bigotimes_{j=m_1}^{0}\!\!\Post_{1j}$\\

\noindent We can apply Lemma \ref{lem-decompose} on each $\symb{OT}$:
\begin{enumerate}
\item For each open transition  $\symb{OT}_p$ in the form: 
$P[Q]_{j_0}\!\models		
\openrule
    {
       \set{\beta_{1p}},\Pred_{1p},\Post_{1p}   }
         {\ostate{s^{l\in L}_{pl}} \OTarrow {\tau} \ostate{s^{l\in L}_{(p+1)l}}}$ \\
If $Q$ moves then we obtain by Lemma \ref{lem-decompose}:\\
$P\models{\openrule
			{
				(\beta_{1pj})^{j\in (J\setminus \Holes(Q)) \cup \{j_0\}}, 
				{\Pred'_{1p}},  
				{\Post'_{1p}}}
			{\ostate{s_{p l}^{l\in L\setminus L_Q}} \OTarrow {\tau}
					\ostate{({s_{(p+1) l}})^{l\in L\setminus L_Q}}}
		}%\]
	\,\text{~~and~~} 
		Q\models{\openrule
			{
				(\beta_{1pj})^{j\in J\cap\Holes(Q)}, {\Pred''_{1p}},  
				{\Post''_{1p}}}
				{\ostate{s_{pl}^{l\in L_Q}} \OTarrow {\alpha_{1p}}
				\ostate{s_{(p+1)l}^{l\in L_Q}}}
				}\\%\]\\
$
such that  $\Pred_{1p} \iff {\Pred'_{1p}}
		\land {\Pred''_{1p}}\land \alpha_{1p}=\beta_{1pj_0}$, $\Post_{1p}={\Post'_{1p}}\uplus 
		{\Post''_{1p}}$ where ${{\Post''_{1p}}}$ is the restriction of $\Post_{1p}$ over variables of $\Leaves(Q)$.\\
Else $Q$ does not move and we have: \\
$P\models{\openrule
			{
				(\beta_{1pj})^{j\in (J\setminus \Holes(Q)) }, 
				{\Pred'_{1p}},  
				{\Post'_{1p}}}
			{\ostate{(s_{p l})^{l\in L\setminus L_Q}} \OTarrow {\tau}
				\ostate{({s}_{(p+1) l})^{l\in L_Q\setminus L_Q}}}
		}$~~and~~ $\ostate{(s_{p})_l^{l\in L_Q}} = \ostate{({s}_{(p+1) l})^{l\in L_Q}} $

\item Similarly, we use the same process on states named $u$.

\item Finally, for the open transition $\symb{OT}$ in the form: $P[Q]_{j_0}	\models \openrule
         {
           \set{\beta_2},\Pred_2,\Post_2 }
         {\ostate{t} \OTarrow {\alpha} \ostate{t'}}$\\
If $Q$ moves then we  obtain by Lemma \ref{lem-decompose}:\\
$
		P\models{\openrule
			{
				(\beta_{2j})^{j\in (J\setminus \Holes(Q)) \cup \{j_0\}}, 
				{\Pred'_2},  
				{\Post'_2}}
			{\ostate{t_l^{l\in L\setminus L_Q}} \OTarrow {\alpha}
				\ostate{t_l'^{\,l\in L\setminus L_Q}}}
		}%\]
	\,\text{~~and~~}
	Q\models{\openrule
			{
				(\beta_{2j})^{j\in J\cap\Holes(Q)}, {\Pred''_2},  
				{\Post''_2}}
			{\ostate{t_l^{l\in L_Q}} \OTarrow {\alpha_2}
				\ostate{t_l'^{\,l\in L_Q}}}
		}%\]
$\\
such that  $\Pred_2 \iff {\Pred'_2}
		\land {\Pred''_2}\land \alpha_2=\beta_{2j_0}$, $\Post_2={\Post'_2}\uplus 
		{\Post''_2}$ where ${\Post''_2}$ is the restriction of $\Post_2$ over variables of $\Leaves(Q)$.

Else $Q$ does not move and we have \\
$
		P\models{\openrule
			{
				(\beta_{2j})^{j\in (J\setminus \Holes(Q)) \cup \{j_0\}}, 
				{\Pred'_2},  
				{\Post'_2}}
			{\ostate{t_l^{l\in L\setminus L_Q}} \OTarrow {\alpha}
				\ostate{t_l'^{\,l\in L\setminus L_Q}}}
		}%\]
	\,\text{~~and~~} \ostate{t_l^{l\in L_Q}} = 
				\ostate{t_l'^{\,l\in L_Q}}$

\end{enumerate}
By using  Lemma \ref{lem-rel-OT-WOT} we can conclude from cases 1, 2 and 3 that we have:
\begin{mathpar}
		P\models{\openrule
			{
				\gamma_j^{j\in (J\setminus \Holes(Q)) \cup \{j_0\}}, 
				\Pred\,',  
				\Post'}
			{\ostate{s_l^{l\in L\setminus L_Q}} \OTWeakarrow {\alpha}
				\ostate{s_l'^{\,l\in L\setminus L_Q}}}
		}%\]
\end{mathpar}
where for all $l\in L$:\\
$\alpha'=\alpha\displaystyle{\subst{\bigotimes_{j=m_1}^{0}\!\!\Post'_{1j}}}$\\
$s_l=s_{0l} \wedge s_{(m_1+1)l}=t_l \wedge t'_l = u_{0l} \wedge u_{(m_2+1)l}=s'_l$
and $\forall j\in (J\setminus \Holes(Q))\cup \{j_0\}$,\\
$\set{\gamma}_j=\displaystyle{\mybigdotcup_{i=0}^{m_1} \vis{\set{\beta_{1ij}}\subst{\bigotimes_{j=i-1}^{0}\!\!\Post'_{1j}}}\dotcup  \vis{\set{\beta_{2j}}\subst{\bigotimes_{j=m_1}^{0}\Post'_{1j}}}} \dotcup\\
~~\qquad \mybigdotcup_{i=0}^{m_2}
\vis{\set{\beta_{3i}} \subst{\bigotimes_{j=i-1}^{0}\!\Post'_{3j}\shortotimes\Post'_2\shortotimes\bigotimes_{j=m_1}^{0}\!\!\Post'_{1j}} }\\
\Pred\,'=\bigwedge_{i=0}^{m_1}\Pred'_{1i}\subst{\bigotimes_{j=i-1}^{0}\!\!\Post'_{1j}}\land\Pred'_2 \subst{\bigotimes_{j=m_1}^{0}\!\!\Post'_{1j}}\land\\ 
~\qquad\qquad\bigwedge_{i=0}^{m_2}\Pred'_{3i}\subst{\bigotimes_{j=i-1}^{0}\!\!\Post'_{3j}\shortotimes\Post'_2\shortotimes\bigotimes_{j=m_1}^{0}\!\!\Post'_{1j}}\\
\Post'=\bigotimes_{j=m_2}^{0}\!\!\Post'_{3j}\shortotimes\Post'_2\shortotimes\bigotimes_{j=m_1}^{0}\!\!\Post'_{1j}$

Concerning $Q$, we consider only the paths for which it moves. So for all states for which we have $\ostate{(s_{p})_l^{l\in L_Q}} = \ostate{({s}_{(p+1) l})^{l\in L_Q}}$, we skip the state $\ostate{({s}_{(p+1) l})^{l\in L_Q}}$ and  we rename all its following states  $\ostate{(s_{p})_l^{l\in L_Q}}$ by $\ostate{({s}_{(p-1) l})^{l\in L_Q}}$. We proceed in the same way as for states named $u$. To simplify the proof, we consider that in case 3, $Q$  moves, i.e, $\ostate{t_l^{l\in L_Q}} \neq \ostate{t_l'^{\,l\in L_Q}}$, else transition 3 of $Q$ should be skipped and the last $s_{p l}$ are equal to the first $u_{0 l}$. So we have: \\ 
$\forall p\! \in\! [0..n_1] Q\models{\openrule
			{
				(\beta_{1pj})^{j\in J\cap\Holes(Q)}, {{\Pred''_{1p}}},  
				{{\Post''_{1p}}}}
				{\ostate{s_{pl}^{l\in L_Q}} \OTarrow {\alpha_{1p}}
				\ostate{s_{(p+1)l}^{l\in L_Q}}}
				}%\]
,$
$ Q\models{\openrule
			{
				(\beta^2_j)^{j\in J\cap\Holes(Q)}, {\Pred''_2},  
				{\Post''_2}}
			{\ostate{t_l^{l\in L_Q}} \OTarrow {\alpha_2}
				\ostate{t_l'^{\,l\in L_Q}}}
		}%\]
$
and
$\forall p \in [0..n_2] Q\models{\openrule
			{
				(\beta_{3pj})^{j\in J\cap\Holes(Q)}, {{\Pred''_{3p}}},  
				{{\Post''_{3p}}}}
				{\ostate{u_{pl}^{l\in L_Q}} \OTarrow {\alpha_{3p}}
				\ostate{u_{(p+1)l}^{l\in L_Q}}}
				}%\]
$\\ 
such that $n_1 \leq m_1$ and $n_2 \leq m_2$\\
By renaming all state names ($s$, $u$ and $t$) with the same state name $v$. We have:

$\forall p \in [0..(n_1\!+\!n_2\!+\!2)]\,\, Q\models{\openrule
			{
				(\beta_{pj})^{j\in J\cap\Holes(Q)}, {{\Pred''_p}},  
				{{\Post''_p}}}
				{\ostate{v_{pl}^{l\in L_Q}} \OTarrow {\alpha_{p}}
				\ostate{v_{(p+1)l}^{l\in L_Q}}}
				}%\]
$\\ 
In this equation, and using cases 1, 2 and 3 above, we have for all $k\in [0\ldots n_1+n_2+2]$, $\beta_{kj_0}=\alpha_k$.

>>>>

\begin{lemma}[Weak OT decomposition]\label{lem-decomposeWOT} 
	Let $\Leaves(Q)=pLTS_l^{l\in L_Q}$; suppose\footnote{Note that the hypotheses of the 
	lemma imply that $Q$ is 
	not a pLTS but a similar lemma can be proven for a pLTS $Q$}:
	\[ P[Q]_{j_0}  
		\models
		{\openrule
			{
				\gamma_j^{j\in J}, \Pred,  
				\Post}
			{\ostate{s_i^{i\in L}} \OTWeakarrow {\alpha}
				\ostate{s_i'^{\, i\in L}}}
		}
	\]
		with  $J\cap\Holes(Q)\neq\emptyset$ or $\exists i\in L_Q.\,s_i\neq s'_i$, i.e. $Q$ takes part in the reduction.  
		 Then there exist $n$, $\Pred\,'$,  
		$\Post\,'$,   and for all $p\in[0..n]$ there exist $\beta_p$, $\alpha_p$, $\Pred_p$, $\Post_p$ and a family $\gamma_{p j}^{j\in J_p}$ and for all $p\in[0..n+1]$ $s_{p i}^{\,i\in L_Q}$. s.t.:\\[-2ex]
		%\[
		\begin{mathpar}
		P\models{\openrule
			{
				\gamma_j^{j\in (J_p\setminus \Holes(Q)) \cup \{j_0\}}, 
				\Pred\,',  
				\Post\,'}
			{\ostate{s_i^{i\in L\setminus L_Q}} \OTWeakarrow {\alpha}
				\ostate{s_i'^{\,i\in L\setminus L_Q}}}
		}%\]
\text{\qquad and \qquad}\gamma_{j_0}=[\beta_0..\beta_n]
	\vspace{-2.2ex}\\\text{and for all $p\in[0..n]$~~}
		%\[
		Q\models{\openrule
			{
				\gamma_{p j}^{j\in J_p}, \Pred_p,  
				\Post_p}
			{\ostate{s_{p i}^{i\in L_Q}} \OTWeakarrow {\alpha_p}
				\ostate{s_{(p+1) i}^{\,i\in L_Q}}}
		}%\]
\\
		\text{and~~}  \bigcup_{p=0}^nJ_{p} = J\cap\Holes(Q) \qquad
 \text{and\qquad} \forall j\in J_p,\,\gamma_j= \mybigdotcup_{p=0}^n \gamma_{p j} \\
 \text{and\quad} \forall i \in L_Q.\, s_{(n+1) i} = s_i'\land s_{0 i} = s_i\\{\hspace{-3ex}}\text{and~~} \Pred = \Pred\,'
		\land \!\!\bigwedge_{p=0}^n((\alpha_p= \beta_p\land \Pred_p)\bigotimes_{i=p-1}^{0}\Post_i) 
\\
\text{and~}
\Post=\Post\,' \uplus \bigotimes_{p=n}^0
		\Post_p  
		\end{mathpar}
where $\Post_p$ only act upon variables of 
		$\Leaves(Q)$.
\end{lemma}

\begin{proof} Suppose that we have: 
\begin{mathpar}
 P[Q]_{j_0} \models \openrule
			{
				{\gamma_j^{j\in J}}, \Pred,  
				\Post}
			{\ostate{s_l^{l\in L}} \OTWeakarrow {\alpha'}
				\ostate{s_l'^{\, l\in L}}} 
\end{mathpar}
By Lemma \ref{lem-rel-OT-WOT} this implies the following: \\			
$ \forall p\! \in [0..m_1]\,		
	P[Q]_{j_0}\!\models		
\openrule
    {
       \set{\beta_{1p}},\Pred_{1p},\Post_{1p}   }
         {\ostate{s^{l\in L}_{pl}} \OTarrow {\tau} \ostate{s^{l\in L}_{(p+1)l}}}$,  $\qquad  P[Q]_{j_0}	\models \openrule
         {
           \set{\beta_2},\Pred_2,\Post_2 }
         {\ostate{t_l^{l\in L}} \OTarrow {\alpha} \ostate{{t'}_l^{l\in L}}}
$ 
\\
and 
 $\forall p \in [0..m_2] \,\, P[Q]_{j_0}\!\models \openrule
         {
           \set{\beta_{3p}},\Pred_{3p}, \Post_{3p}   }
         {\ostate{u^{l\in L}_{pl}} \OTarrow {\tau} \ostate{u^{l\in L}_{(p+1)l}}}
$\\
where\\
$\alpha'=\alpha\displaystyle{\subst{\bigotimes_{j=m_1}^{0}\!\!\Post_{1j}}}$\\
 for all $l\in L$: $s_l=s_{0 l} \wedge s_{(m_1+1) l}=t_l \wedge t'_l = u_{0 l} \wedge u_{(m_2+1) l}=s'_l$\\
$\displaystyle{
\gamma_j^{j\in J}=\mybigdotcup_{i=0}^{m_1} \vis{\set{\beta_{1i}}\subst{\bigotimes_{j=i-1}^{0}\!\! \Post_{1j}}}\dotcup  \vis{\set{\beta_2}\subst{\bigotimes_{j=m_1}^{0}\Post_{1j}}} \dotcup \mybigdotcup_{i=0}^{m_2} \vis{\set{\beta_{3i}} \subst{\bigotimes_{j=i-1}^{0}\!\Post_{3j}\shortotimes\Post_2\shortotimes\bigotimes_{j=m_1}^{0}\!\!\Post_{1j}} }}
\\
\Pred=\bigwedge_{i=0}^{m_1}\Pred_{1i}\subst{\bigotimes_{j=i-1}^{0}\!\!\Post_{1j}}\land\Pred_2 \subst{\bigotimes_{j=m_1}^{0}\!\!\Post_{1j}}\land\\ 
~\qquad\quad\bigwedge_{i=0}^{m_2}\Pred_{3i}\subst{\bigotimes_{j=i-1}^{0}\!\!\Post_{3j}\shortotimes\Post_2\shortotimes\bigotimes_{j=m_1}^{0}\!\!\Post_{1j}}\\
\Post=\bigotimes_{j=m_2}^{0}\!\!\Post_{3j}\shortotimes\Post_2\shortotimes\bigotimes_{j=m_1}^{0}\!\!\Post_{1j}$\\

\noindent We can apply Lemma \ref{lem-decompose} on each $\symb{OT}$:
\begin{enumerate}
\item For each open transition  $\symb{OT}_p$ in the form ($\set{\beta_{1p}}=\beta_{1pj}^{j\in J_{1p}}$): 
$P[Q]_{j_0}\!\models		
\openrule
    {
       {\beta_{1pj}^{j\in J_{1p}}},\Pred_{1p},\Post_{1p}   }
         {\ostate{s^{l\in L}_{pl}} \OTarrow {\tau} \ostate{s^{l\in L}_{(p+1)l}}}$ \\
If $Q$ moves then we obtain by Lemma \ref{lem-decompose}:\\
$P\models{\openrule
			{
				(\beta_{1pj})^{j\in (J_{1p}\setminus \Holes(Q)) \cup \{j_0\}}, 
				{\Pred'_{1p}},  
				{\Post'_{1p}}}
			{\ostate{s_{p l}^{l\in L\setminus L_Q}} \OTarrow {\tau}
					\ostate{({s_{(p+1) l}})^{l\in L\setminus L_Q}}}
		}%\]
	\,\text{~~and~~} 
		Q\models{\openrule
			{
				(\beta_{1pj})^{j\in J_{1p}\cap\Holes(Q)}, {\Pred''_{1p}},  
				{\Post''_{1p}}}
				{\ostate{s_{pl}^{l\in L_Q}} \OTarrow {\alpha_{1p}}
				\ostate{s_{(p+1)l}^{l\in L_Q}}}
				}\\%\]\\
$
such that  $\Pred_{1p} \iff {\Pred'_{1p}}
		\land {\Pred''_{1p}}\land \alpha_{1p}=\beta_{1pj_0}$, $\Post_{1p}={\Post'_{1p}}\uplus 
		{\Post''_{1p}}$ where ${{\Post''_{1p}}}$ is the restriction of $\Post_{1p}$ over variables of $\Leaves(Q)$.\\
Else $Q$ does not move and we have: \\
$P\models{\openrule
			{
				(\beta_{1pj})^{j\in (J_{1p}\setminus \Holes(Q)) }, 
				{\Pred'_{1p}},  
				{\Post'_{1p}}}
			{\ostate{(s_{p l})^{l\in L\setminus L_Q}} \OTarrow {\tau}
				\ostate{({s}_{(p+1) l})^{l\in L\setminus L_Q}}}
		}$~~and~~ $\ostate{(s_{p})_l^{l\in L_Q}} = \ostate{({s}_{(p+1) l})^{l\in L_Q}} $

\item Similarly, we have similar open transitions on states $u_{pl}$ (for the final $\tau$ transitions).

\item Finally, for the open transition $\symb{OT}$ in the form ($\set{\beta_{2}}=\beta_{2j}^{j\in J_2}$): $P[Q]_{j_0}	\models \openrule
         {
           \beta_{2j}^{j\in J_2},\Pred_2,\Post_2 }
         {\ostate{t} \OTarrow {\alpha} \ostate{t'}}$\\
If $Q$ moves then we  obtain by Lemma \ref{lem-decompose}:\\
$
		P\models{\openrule
			{
				(\beta_{2j})^{j\in (J_2\setminus \Holes(Q)) \cup \{j_0\}}, 
				{\Pred'_2},  
				{\Post'_2}}
			{\ostate{t_l^{l\in L\setminus L_Q}} \OTarrow {\alpha}
				\ostate{t_l'^{\,l\in L\setminus L_Q}}}
		}%\]
	\,\text{~~and~~}
	Q\models{\openrule
			{
				(\beta_{2j})^{j\in J_2\cap\Holes(Q)}, {\Pred''_2},  
				{\Post''_2}}
			{\ostate{t_l^{l\in L_Q}} \OTarrow {\alpha_2}
				\ostate{t_l'^{\,l\in L_Q}}}
		}%\]
$\\
such that  $\Pred_2 \iff {\Pred'_2}
		\land {\Pred''_2}\land \alpha_2=\beta_{2j_0}$, $\Post_2={\Post'_2}\uplus 
		{\Post''_2}$ where ${\Post''_2}$ is the restriction of $\Post_2$ over variables of $\Leaves(Q)$.

Else $Q$ does not move and we have \\
$
		P\models{\openrule
			{
				(\beta_{2j})^{j\in (J_2\setminus \Holes(Q)) \cup \{j_0\}}, 
				{\Pred'_2},  
				{\Post'_2}}
			{\ostate{t_l^{l\in L\setminus L_Q}} \OTarrow {\alpha}
				\ostate{t_l'^{\,l\in L\setminus L_Q}}}
		}%\]
	\,\text{~~and~~} \ostate{t_l^{l\in L_Q}} = 
				\ostate{t_l'^{\,l\in L_Q}}$

\end{enumerate}
By using  Lemma \ref{lem-rel-OT-WOT}, denoting $\displaystyle{J=\bigcup_{i=0}^{m_1}J_{1i}\cup J_2\cup \bigcup_{i=0}^{m_2}J_{3i}}$, we can conclude from cases 1, 2 and 3 that we have:
\begin{mathpar}
		P\models{\openrule
			{
				\gamma_j^{j\in (J\setminus \Holes(Q)) \cup \{j_0\}}, 
				\Pred\,',  
				\Post'}
			{\ostate{s_l^{l\in L\setminus L_Q}} \OTWeakarrow {\alpha}
				\ostate{s_l'^{\,l\in L\setminus L_Q}}}
		}%\]
\end{mathpar}
where:\\
$\alpha'=\alpha\displaystyle{\subst{\bigotimes_{j=m_1}^{0}\!\!\Post'_{1j}}}$\\
 for all $l\in L$: 
$s_l=s_{0l} \wedge s_{(m_1+1)l}=t_l \wedge t'_l = u_{0l} \wedge u_{(m_2+1)l}=s'_l$
and \\%$\forall j\in (J\setminus \Holes(Q))\cup \{j_0\}$,\\
$\set{\gamma}_j=\displaystyle{\mybigdotcup_{i=0}^{m_1} \vis{\set{\beta_{1i}}\subst{\bigotimes_{j=i-1}^{0}\!\!\Post'_{1j}}}\dotcup  \vis{\set{\beta_{2}}\subst{\bigotimes_{j=m_1}^{0}\Post'_{1j}}}} \dotcup\\
~~\qquad \mybigdotcup_{i=0}^{m_2}
\vis{\set{\beta_{3i}} \subst{\bigotimes_{j=i-1}^{0}\!\Post'_{3j}\shortotimes\Post'_2\shortotimes\bigotimes_{j=m_1}^{0}\!\!\Post'_{1j}} }\\
\Pred\,'=\bigwedge_{i=0}^{m_1}\Pred'_{1i}\subst{\bigotimes_{j=i-1}^{0}\!\!\Post'_{1j}}\land\Pred'_2 \subst{\bigotimes_{j=m_1}^{0}\!\!\Post'_{1j}}\land\\ 
~\qquad\qquad\bigwedge_{i=0}^{m_2}\Pred'_{3i}\subst{\bigotimes_{j=i-1}^{0}\!\!\Post'_{3j}\shortotimes\Post'_2\shortotimes\bigotimes_{j=m_1}^{0}\!\!\Post'_{1j}}\\
\Post'=\bigotimes_{j=m_2}^{0}\!\!\Post'_{3j}\shortotimes\Post'_2\shortotimes\bigotimes_{j=m_1}^{0}\!\!\Post'_{1j}$

Concerning $Q$, we reduce the sequence of OTs to a path for which it moves in all steps. In other words, if there is $Q$ does not move at step $q$, then we have $\ostate{s_{q_l}^{l\in L_Q}} = \ostate{{s}_{(q+1) l}^{l\in L_Q}}$ , then we skip the state $\ostate{{s}_{(q+1) l}^{l\in L_Q}}$, i.e.  we rename all the following states  $\ostate{s_{p l}^{l\in L_Q}}$ where $p\geq q+1$ by $\ostate{{s}_{(p-1) l}^{l\in L_Q}}$. Note that if $Q$ does an OT staying at the same state, we keep this necessary OT. We proceed in the same way  for states named $u$. To simplify the proof, we suppose that in case 3, $Q$  moves, else transition 3 of $Q$ should be skipped and the last $s_{p l}$ are equal to the first $u_{0 l}$. So we have: \\ 
$\forall p\! \in\! [0..n_1] Q\models{\openrule
			{
				(\beta'_{1pj})^{j\in J\cap\Holes(Q)}, {{\Pred''_{1p}}},  
				{{\Post''_{1p}}}}
				{\ostate{s_{pl}^{l\in L_Q}} \OTarrow {\alpha_{1p}}
				\ostate{s_{(p+1)l}^{l\in L_Q}}}
				}%\]
,$
$ Q\models{\openrule
			{
				(\beta'_{2 j})^{j\in J\cap\Holes(Q)}, {\Pred''_2},  
				{\Post''_2}}
			{\ostate{t_l^{l\in L_Q}} \OTarrow {\alpha_2}
				\ostate{t_l'^{\,l\in L_Q}}}
		}%\]
$
and
$\forall p \in [0..n_2] Q\models{\openrule
			{
				(\beta'_{3pj})^{j\in J\cap\Holes(Q)}, {{\Pred''_{3p}}},  
				{{\Post''_{3p}}}}
				{\ostate{u_{pl}^{l\in L_Q}} \OTarrow {\alpha_{3p}}
				\ostate{u_{(p+1)l}^{l\in L_Q}}}
				}%\]
$\\ 
such that $n_1 \leq m_1$ and $n_2 \leq m_2$.\\
By renaming all state names ($s$, $u$ and $t$) with the same state name $v$. We have:

$\forall p \in [0..(n_1\!+\!n_2\!+\!2)]\,\, Q\models{\openrule
			{
				\beta_{pj}^{j\in J\cap\Holes(Q)}, {{\Pred''_p}},  
				{{\Post''_p}}}
				{\ostate{v_{pl}^{l\in L_Q}} \OTarrow {\alpha_{p}}
				\ostate{v_{(p+1)l}^{l\in L_Q}}}
				}%\]
$\\ 
In this equation, and using cases 1, 2 and 3 above, we have for all $k\in [0\ldots n_1+n_2+2]$, then there is an action $\beta$ such that $\beta=\beta_{1p j_0}$ s.t. $j_0\in J_{1p}$, or $\beta=\beta_{2 j_0}$ with $j_0\in J_{2}$, or $\beta=\beta_{3p j_0}$ s.t. $j_0\in J_{3p}$, where $\beta=\alpha_k$, additionally the different $\beta$ are ordered by following the OTs, somehow performing the same re-indexing as  the removal of steps where $Q$ does not move above. Overall we have\footnote{under the assumption written above, i.e. that $Q$ moves in the middle OT, i.e. $j_0\in J_{2}$}:
\[
[\beta_{1 p j_0}|j_0\in J_{1p}]\dotcup [\beta_{2 j_0}] \dotcup [\beta_{3 p j_0}|j_0\in J_{3p}] = [\alpha_0..\alpha_{n_1+n_2+2}]
\]
